Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-22 sections/eval.tex
Update on Overleaf.

To get a sense of the Python Array API, we provide a few examples of their

\subsubsection{Finch Logic}

\begin{align*}
    \finchreorder(name, idxs...) := 
\end{align*}

>>>>

\subsubsection{Finch Logic}
The Finch Logic language takes inspiration from relational algebra while incorporating the ordered nature of dimensions in sparse tensors. In this analogy,

\begin{align*}
    \finchplan(queries...) &  \quad\quad\quad \finchquery(name, expr) & \finchreorder(expr, idxs...)\\
    \finchrelabel(expr, idxs...)& \quad\quad\quad \finchmapjoin(op, exprs...)  & \finchaggregate(op, expr)\\
    \quad\quad\quad & \quad\quad\quad \finchtable(tns, idxs...)\quad\quad\quad  & \quad\quad\quad \\
\end{align*}
